Warming Degrees and Flowering Trees

### 2025-04-02 paper/paper.qmd
fixed modeling amended intro with implications summary

---
title: "Your Paper Title"
subtitle: "Understanding Temperature's Role in Earlier Cherry Blossom Blooming Times in Kyoto, Japan"
author:
    - Luca Carnegie
    - Chris Lu
    - Russell Luchin
    - Randall Ni
abstract:
    This is the abstract of your paper. Write a brief summary of your research,
    including your objectives, methods, key results, and main conclusions.
    Keep it concise but informative.
format:
    pdf:
        documentclass: article
        papersize: letter
        toc: true
        number-sections: true
        colorlinks: true
        fig-cap-location: bottom
        tbl-cap-location: top
        fontsize: "12"
        geometry: "margin=1.2in" # print margins (change if wanting to)
bibliography: "references.bib"
execute:
    echo: false  # Hide code by default
    warning: false
    message: false
    jupyter: "python"
nocite: "@*" # display all references by default
thanks: "Code and workflow available at: https://github.com/lcarnegie/sakura" 
---

```{python}
# Import necessary libraries 
import pandas as pd
import numpy as np
import matplotlib.pyplot as plt
import matplotlib.dates as mdates
import seaborn as sns
import statsmodels.api as sm
import numpy as np
from matplotlib.colors import LinearSegmentedColormap
from matplotlib.ticker import MaxNLocator
from datetime import datetime

@@

We seek to answer the question of whether warmer temperatures lead to earlier blooming times. To do this, we analyse and model the nearly 1200-year record compiled by @Aono2010 in tandem with modern data compiled by the Japanese Meteorological Agency (JMA), collected and compiled together by @Cookson. @sec-lit-review does a broad review of existing work surrounding cherry blossoms, their significance, and efforts to understand their behaviour related to climate. @sec-data covers the data sources, methodology, and conducts an exploratory analysis of the dataset. @sec-model proposes a model of cherry blossom flowering day as a function of mean March temperature in Kyoto and lists its results. @sec-discussion critically examines the data and results, comes to several conclusions about the dataset, and proposes new areas of exploration. This analysis highlights the need for... \[FILL IN AT END\]

@@

With the modern data, @Cookson combined average monthly temperatures and blooming date in a single dataset for several cities across Japan. We filtered this data to solely Kyoto, with average march temperatures to match the historical data. This created a dataset with 67 observations from the year 1953-2015. A sample can be seen in @tbl-modern.

In our data exploration, the `matplotlib` [@matplotlib] and `seaborn` packages were used to visualize the data.

Boilerplate table

```{python}

Boilerplate Fig

```{python}

```{python}
#| label: tbl-historical
#| tbl-cap: "Historical Cherry Blossom Blooming"

@@

```{python}
#| label: tbl-modern
#| tbl-cap: "Modern Cherry Blossom Blooming"

@@

The datasets were first explored chronologically, beginning with the historical data and ending with the modern data.

```{python}

@@

@@

## Implications of Findings

@@

## Robustness Checks

>>>>

---
title: "Warming Degrees and Flowering Trees"
subtitle: "Understanding Temperature's Role in Earlier Cherry Blossom Blooming Times in Kyoto, Japan"
author:
    - Luca Carnegie
    - Chris Lu
    - Russell Luchin
    - Randall Ni
abstract:
    This is the abstract of your paper. Write a brief summary of your research,
    including your objectives, methods, key results, and main conclusions.
    Keep it concise but informative.
format:
    pdf:
        documentclass: article
        papersize: letter
        toc: true
        number-sections: true
        colorlinks: true
        fig-cap-location: bottom
        tbl-cap-location: top
        fontsize: "12"
        geometry: "margin=1.2in" # print margins (change if wanting to)
bibliography: "references.bib"
execute:
    echo: false  # Hide code by default
    warning: false
    message: false
    jupyter: "python"
nocite: "@*" # display all references by default
thanks: "Code and workflow available at: https://github.com/lcarnegie/sakura" 
---

```{python}
#| label: data-setup

# Import necessary libraries 
import pandas as pd
import numpy as np
import matplotlib.pyplot as plt
import matplotlib.dates as mdates
import seaborn as sns
import statsmodels.api as sm
import numpy as np
from matplotlib.colors import LinearSegmentedColormap
from matplotlib.ticker import MaxNLocator
from datetime import datetime

@@

We seek to answer the question of whether warmer temperatures lead to earlier blooming times. To do this, we analyse and model the nearly 1200-year record compiled by @Aono2010 in tandem with modern data compiled by the Japanese Meteorological Agency (JMA), collected and compiled together by @Cookson. @sec-lit-review does a broad review of existing work surrounding cherry blossoms, their significance, and efforts to understand their behaviour related to climate. @sec-data covers the data sources, methodology, and conducts an exploratory analysis of the dataset. @sec-model proposes a model of cherry blossom flowering day as a function of mean March temperature in Kyoto and lists its results. @sec-discussion critically examines the data and results, comes to several conclusions about the dataset, and proposes new areas of exploration. This analysis highlights several conclusions. First, temperature changes will have consequential effects for wildlife that function around the timing of blooming *sakura*. Next, social celebrations such as *hanami* will be impacted, changing the timing of a once-constant annual event. Finally, there is a need for more a more comprehensive inquiry into the determinants of cherry blossom blooming in Japan more generally, involving more covariates, so that more robust predictions of *sakura* blooming in Kyoto can be made. By gathering more data to make better predictions, the city of Kyoto will better be able to weather climate change and bridge their cherished traditions into the future.

@@

```{python}
#| label: tbl-historical-data
#| tbl-cap: "Historical Cherry Blossom Blooming"

@@

With the modern data, @Cookson combined average monthly temperatures and blooming date in a single dataset for several cities across Japan. We filtered this data to solely Kyoto, and solely average march temperatures to match the historical data from @Aono2010. This created a dataset with 67 observations ranging from 1953 to 2015. A sample can be seen in @tbl-modern.

```{python}
#| label: tbl-modern-data
#| tbl-cap: "Modern Cherry Blossom Blooming"

@@

In our data exploration, the `matplotlib` [@matplotlib] and `seaborn` packages were used to visualize and explore the data. The datasets were first explored chronologically, beginning with the historical data and ending with the modern data.

@@

```{python}
#| label: historic-temp-yr-scatter
#| message: false
#| echo: false
#| warning: false
#| fig-cap: WRITE SOMETHING
#| fig-align: center

@@

## Ecological Implications

## Cultural Implications

@@
